---
title: "Cpu Performance Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r, echo=FALSE}
cpuData <- read.csv("machine.csv")
```
###Instructor :

- Pasillas Diáz José Ramon


###Authors :

- David del real
- Kevin Salmon
- Esteban Garcia
- Irwin Trujillo

##Index

-  Introduction.
-  Exploratory Analysis.
-  Conclucion.


##1.- Introduction.

This dataset is a compilation of several processors and their characteristics.

The purpose is to find an estimate of the performance of these processors and compare it with the data published by the hardware manufacturers.

#Exploratory Analysis

##Descripcion de Variables

- Vendor Name (No need for an explanation here).
- Model.
- MYCT: It's the machine cycle in nanoseconds.
- MMIN: Minimum of memory in kilobytes.
- MMAX: Maximum memory in kilobytes.
- CACH: Cache size in kilobytes.
- CHMIN: Minimal channels in units.
- CHMAX: Maximum channels in units.
- PRP: Relative Performance Published
- ERP: Estimated relative performance.

##Summary
```{r}
summary(cpuData)
```

##Boxplots
##Sezgo
##Histograms
##Quartiles
##Correlation

Correlation is a statistical function that allows to find the linear dependence of two random variables X and Y.

The correlation coefficient r can have a range between -1 and 1, being one (1), a perfect dependency, minus one (-1) the anti-correlation, and 0 being null correlation.

As the coefficient increases, it means that Y increases when X does, the reverse is true as it decreases, the increase is smaller, and if it becomes negative, it becomes a decrease.

Since the dataset contains two non-numeric attributes, we first need to remove those columns:


```{r Correlacion}

#Removing non-numeric columns
cpuMatrix <- cpuData[-1]
cpuMatrix <- cpuMatrix[-1]
```

Once the non-numeric columns have been removed, we can use the cor () function to find the correlation coefficients of the matrix.
```{r}
# Matrix mapping

# We can see that according to their correlation coefficients, when time-based cycles are smaller, all other variables tend to increase slightly. 
cor(cpuMatrix)

```


##Scatterplot
Las graficas de dispersion sirven para mostrar la dependencia entre dos variable X y Y. Pueden ser una manera de visualizar la correlacion de dos variables.
```{r}

#Grafica de scatter `para la correlacion de PRP y MMAX`
plot(cpuMatrix$PRP,cpuMatrix$MMAX,xlab="Rendimiento relativo publicado",ylab = "Memoria maxima en KB")


#Podemos apreciar, cuando la memoria maxima aumenta, tambien el rendimiento relativo publicado incrementa

#Grafica de scatter `para la correlacion de ERP y MMAX`
plot(cpuMatrix$ERP,cpuMatrix$MMAX,xlab = "Rendimiento relativo estimado",ylab = "Memoria Maxima en KB")
#La estimacion de rendimiento tambien aumenta linearmente con la memoria en KB

#Grafica de scatter `para la correlacion de PRP y ERP`
plot(cpuMatrix$ERP,cpuMatrix$PRP,xlab = "Rendimiento relativo estimado",ylab="Rendimiento relativo publicado")
#La relacion entre Lo estimado y lo publicado. Lo optimo deberia ser que la correlacion fuera perfecta, significaria que los datos publicados son congruentes con los datos estimados.
```


#Conclusión


