---
title: "Cpu Performance Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r, echo=FALSE}
cpuData <- read.csv("machine.csv")
```
##Instructor :

- Pasillas Diáz José Ramon


##Authors :

- David del real
- Kevin Salmon
- Esteban Garcia
- Irwin Trujillo

##Index

-  Introduction.
-  Exploratory Analysis.
-  Conclucion.


##1.- Introduction.

This dataset is a compilation of several processors and their characteristics.

The purpose is to find an estimate of the performance of these processors and compare it with the data published by the hardware manufacturers.

#Exploratory Analysis

##Variables Overview

- Vendor.Name. The name of the manufacturer.
- Model. The model of the Cpu
- MYCT: It's the machine cycle in nanoseconds.
- MMIN: Minimum of memory in kilobytes.
- MMAX: Maximum memory in kilobytes.
- CACH: Cache size in kilobytes.
- CHMIN: Minimal channels in units.
- CHMAX: Maximum channels in units.
- PRP: Relative Performance Published
- ERP: Estimated relative performance.

##Summary
```{r}
summary(cpuData)
```

##Boxplots
##Bias
##Histograms
##Cuartiles
##Correlation

Correlation is a statistical function that allows to find the linear dependence of two random variables X and Y.

The correlation coefficient r can have a range between -1 and 1, being one (1), a perfect dependency, minus one (-1) the anti-correlation, and 0 being null correlation.

As the coefficient increases, it means that Y increases when X does, the reverse is true as it decreases, the increase is smaller, and if it becomes negative, it becomes a decrease.

Since the dataset contains two non-numeric attributes, we first need to remove those columns:


```{r Correlacion}

#Removing non-numeric columns
cpuMatrix <- cpuData[-1]
cpuMatrix <- cpuMatrix[-1]
```

Once the non-numeric columns have been removed, we can use the cor () function to find the correlation coefficients of the matrix.
```{r}
# Matrix mapping

# We can see that according to their correlation coefficients, when time-based cycles are smaller, all other variables tend to increase slightly. 
cor(cpuMatrix)

```


##Scatterplot
The dispersion graphs serve to show the dependence between two variables X and Y. They can be a way to visualize the correlation of two variables.
```{r}

#Scatterplot for the correlation of PRP and MMAX.`
plot(cpuMatrix$PRP,cpuMatrix$MMAX,xlab="Relative performance published",ylab = "Maximum memory in KB")


#We can appreciate, when the maximum memory increases, also the published relative performance increases

#Scatterplot for the correlation of ERP and MMAX.
plot(cpuMatrix$ERP,cpuMatrix$MMAX,xlab = "Estimated relative performance",ylab = "Maximum memory in KB")

#The performance estimate also increases linearly with memory in KB

#Scatterplot for the correlation of PRP and ERP.
plot(cpuMatrix$ERP,cpuMatrix$PRP,xlab = "Estimated relative performance",ylab="Relative performance published")

#The relationship between the estimated and the published.
#The optimum should be that the correlation is perfect, it would mean that the published data are congruent with the estimated data.
```


#Conclusión


