---
title: "Cpu Performance Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r, echo=FALSE}
cpuData <- read.csv("machine.csv")
```
##Instructor :

- Pasillas Di?z Jos? Ramon


##Authors :

- David del real
- Kevin Salmon
- Esteban Garcia
- Irwin Trujillo

##Index

-  Introduction.
-  Exploratory Analysis.
-  Conclucion.


##1.- Introduction.

This dataset is a compilation of several processors and their characteristics.

The purpose is to find an estimate of the performance of these processors and compare it with the data published by the hardware manufacturers.

#Exploratory Analysis

##Variables Overview

- Vendor.Name. The name of the manufacturer.
- Model. The model of the Cpu
- MYCT: It's the machine cycle in nanoseconds.
- MMIN: Minimum of memory in kilobytes.
- MMAX: Maximum memory in kilobytes.
- CACH: Cache size in kilobytes.
- CHMIN: Minimal channels in units.
- CHMAX: Maximum channels in units.
- PRP: Relative Performance Published
- ERP: Estimated relative performance.

##Summary
```{r}
summary(cpuData)
```

##Boxplots
##Bias

##Histograms
##we can se in the next histograms that the distribution favors to the left wich makes sense. this must be the comercial cpu's and to the rigth we see cpu's that where developed for more specialiced purposes
```{r}

hist(cpuData$MMAX, xlab = 'Max memory in kb',main = 'Histogram of max memory in kb', border = 'black',col = 'orange' )
hist(cpuData$MMIN, xlab = 'Min memory in kb',main = 'Histogram of min memory in kb', border = 'black',col = 'orange' )
hist(cpuData$CHMAX, xlab = 'Cache in kb',main = 'Histogram of Cache in kb', border = 'black',col = 'red' )

```
##Histogram of machine cycle in nanoseconds
```{r}
hist(cpuData$MYCT, xlab = 'machine Cycle in kb/nanoseconds',main = 'Histogram of Cycle', border = 'black',col = 'green' )
```


##The next histograms show the performance, both estimated and publicated

```{r}
hist(cpuData$PRP, xlab = 'Publicated performance in kb/nanoseconds',main = 'Histogram of Publicated performance', border = 'black',col = 'blue' )
hist(cpuData$ERP, xlab = 'Estimated performance in kb/nanoseconds',main = 'Histogram of Public performance', border = 'black',col = 'blue' )
```

#Quartiles
###First lets sort our dataset
```{r}
sortedCpuData <- data.frame(MYCT = (sort(cpuData$MYCT)), MMIN = (sort(cpuData$MMIN)),MMAX = (sort(cpuData$MMAX)),CACH = (sort(cpuData$CACH)),CHMIN = (sort(cpuData$CHMIN)),CHMAX = (sort(cpuData$CHMAX)),PRP = (sort(cpuData$PRP)),ERP = (sort(cpuData$ERP)))
head(sortedCpuData)
```
###Next let's obtain the quartiles
MACHINE CYCLE  
Minimum value is 17 while the maximum value is 1500 and the median 110
lowest fall below 50 kb/nanoseconds 
highest are above 225 kb/nanoseconds
and the rest fall between them being split by 110 kb/nanoseconds
```{r}
quantile(sortedCpuData$MYCT)
```

MIN MEMORY IN KB  
Minimum value is 64 while the maximum value is 32000 and the median 2000
lowest fall below 768 kb 
highest are above 4000 kb
and the rest fall between them being split by 200 kb
```{r}
quantile(sortedCpuData$MMIN)
```

MAX MEMORY IN KB   
Minimum value is 64 while the maximum value is 64000 and the median 8000
lowest fall below 4000 kb 
highest are above 16000 nanoseconds
and the rest fall between them being split by 8000 kb
```{r}
quantile(sortedCpuData$MMAX)
```

PUBLICATED PERFORMANCE  
Minimum value is 6 while the maximum value is 1150 kb/nanoseconds and the median 50 kb/nanoseconds
lowest fall below 27  kb/nanoseconds
highest are above 113 kb/nanoseconds
and the rest fall between them being split by 50 kb/nanoseconds
```{r}
quantile(sortedCpuData$PRP)
```

ESTIMATED PERFORMANCE  
Minimum value is 15 kb/nanoseconds while the maximum value is 1238 and the median 45 kb/nanoseconds
lowest fall below 28  kb/nanoseconds
highest are above 101 kb/nanoseconds
and the rest fall between them being split by 45 kb/nanoseconds
```{r}
quantile(sortedCpuData$ERP)
```

##Boxplot
A box plot or boxplot is a method for graphically depicting groups of numerical data through their quartiles.

Box plots may also have lines extending vertically from the boxes (whiskers) indicating variability outside the upper and lower quartiles, 

hence the terms box-and-whisker plot and box-and-whisker diagram. 

```{r Boxplots}
#Boxplot of machine cycle time
boxplot(cpuData$MYCT,
        main = "Boxplot of Machine cycle time",
        ylab = "Nanosenconds (Ns.)") 

#Boxplot of the minimum main memory
boxplot(cpuData$MMIN,
        main = "Boxplot of Minimum main memory",
        ylab = "Kilobytes (Kb.)")

#Boxplot of the maximum main memory
boxplot(cpuData$MMAX,
        main = "Boxplot of Maximum main memory",
        ylab = "Kilobytes (Kb.)") 

#boxplot of the cache memory
boxplot(cpuData$CACH,
        main = "Boxplot of cache memory",
        ylab = "Kilobytes (Kb.)") 

#boxplot of the maximum main memory
boxplot(cpuData$MMAX,
        main = "Boxplot of Maximum main memory",
        ylab = "Kilobytes (Kb.)")

#boxplot of the minimum channels
boxplot(cpuData$CHMIN,
        main = "Boxplot of Minimum channels",
        ylab = "Units (U.)")

#boxplot of the maximum channels
boxplot(cpuData$CHMAX,
        main = "Boxplot of Maximum channels",
        ylab = "Units (U.)")

#boxploot of the relative performance
boxplot(cpuData$PRP,
        main = "Boxplot of published relative performance",
        ylab = "Performance (P.)") 

#boxplot of the estimated relative performance from original article
boxplot(cpuData$MMAX,
        main = "Boxplot of estimated relative performance from original article",
        ylab = "Performance (P.)") 
```

Skewness is a term in statistics used to describes asymmetry from the normal distribution in 

a set of statistical data. Skewness can come in the form of negative skewness or positive skewness, 

depending on whether data points are skewed to the left and negative, or to the right and positive of the data average. 

A dataset that shows this characteristic differs from a normal bell curve.

```{r Skewness}
library(e1071)

##Skewness of cycle time
skewness(cpuData$MYCT)

##Skewness of minimum main memory
skewness(cpuData$MMIN)

##Skewness of maximum main memory
skewness(cpuData$MMAX)

##Skewness of cache of memory
skewness(cpuData$CACH)

##Skewness of minimum channels
skewness(cpuData$CHMIN)

##Skewness of maximum channels
skewness(cpuData$CHMAX)

##Skewness of relative performance
skewness(cpuData$PRP)

##Skewness of estimated relative performance
skewness(cpuData$ERP)
```

##Correlation

Correlation is a statistical function that allows to find the linear dependence of two random variables X and Y.

The correlation coefficient r can have a range between -1 and 1, being one (1), a perfect dependency, minus one (-1) the anti-correlation, and 0 being null correlation.

As the coefficient increases, it means that Y increases when X does, the reverse is true as it decreases, the increase is smaller, and if it becomes negative, it becomes a decrease.

Since the dataset contains two non-numeric attributes, we first need to remove those columns:


```{r Correlacion}

#Removing non-numeric columns
cpuMatrix <- cpuData[-1]
cpuMatrix <- cpuMatrix[-1]
```

Once the non-numeric columns have been removed, we can use the cor () function to find the correlation coefficients of the matrix.
```{r}
# Matrix mapping

# We can see that according to their correlation coefficients, when time-based cycles are smaller, all other variables tend to increase slightly. 
cor(cpuMatrix)

```


##Scatterplot
The dispersion graphs serve to show the dependence between two variables X and Y. They can be a way to visualize the correlation of two variables.
```{r}

#Scatterplot for the correlation of PRP and MMAX.`
plot(cpuMatrix$PRP,cpuMatrix$MMAX,xlab="Relative performance published",ylab = "Maximum memory in KB")


#We can appreciate, when the maximum memory increases, also the published relative performance increases

#Scatterplot for the correlation of ERP and MMAX.
plot(cpuMatrix$ERP,cpuMatrix$MMAX,xlab = "Estimated relative performance",ylab = "Maximum memory in KB")

#The performance estimate also increases linearly with memory in KB

#Scatterplot for the correlation of PRP and ERP.
plot(cpuMatrix$ERP,cpuMatrix$PRP,xlab = "Estimated relative performance",ylab="Relative performance published")

#The relationship between the estimated and the published.
#The optimum should be that the correlation is perfect, it would mean that the published data are congruent with the estimated data.
```

#Conclusion
=======



