---
title: "Cpu Performance Analysis"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r, echo=FALSE}
cpuData <- read.csv("machine.csv")
```
## Cpu Performance Analysis


Instructor :

Pasillas Diaz Jose Ramon.

Authors:

- David del Real.
- Kevin Salmon.
- Esteban Garcia.
- Irwin Trujillo.

## Problem description

When we buy a processor, we usually rely on the processing speed that the manufacturer indicated as valid.

But, is there any way to know which vendors are loyal to their customers and actually deliver them an expected processing speed?

We used a dataset thath help to answer the question.
 

## Summary

```{r, echo = TRUE}
summary(cpuData)
```


##Boxplots of the data
A boxplot is a method for graphically depicting groups of numerical data through their quartiles.
Boxplot of machine cycle time
```{r plotbox}
quantile(cpuData$MYCT)
boxplot(cpuData$MYCT,
        main = "Boxplot of Machine cycle time",
        ylab = "Nanosenconds (Ns.)") 

```
  
  

Boxplot of the minimum main memory
```{r}
quantile(cpuData$MMIN)
boxplot(cpuData$MMIN,
        main = "Boxplot of Minimum main memory",
        ylab = "Kilobytes (Kb.)")
```
  
  

Boxplot of the maximum main memory
```{r}
quantile(cpuData$MMAX)
boxplot(cpuData$MMAX,
        main = "Boxplot of Maximum main memory",
        ylab = "Kilobytes (Kb.)") 
```

  
  
boxplot of the cache memory
```{r}
quantile(cpuData$CACH)
boxplot(cpuData$CACH,
        main = "Boxplot of cache memory",
        ylab = "Kilobytes (Kb.)") 
```
  
  

boxplot of the maximum main memory
```{r }
quantile(cpuData$MMAX)
boxplot(cpuData$MMAX,
        main = "Boxplot of Maximum main memory",
        ylab = "Kilobytes (Kb.)")
```
  
  

boxplot of the minimum channels
```{r}
quantile(cpuData$CHMIN)
boxplot(cpuData$CHMIN,
        main = "Boxplot of Minimum channels",
        ylab = "Units (U.)")
```

  
  
boxplot of the maximum channels
```{r}
quantile(cpuData$CHMAX)
boxplot(cpuData$CHMAX,
        main = "Boxplot of Maximum channels",
        ylab = "Units (U.)")
```
  
  
  
boxplot of the relative performance
```{r}
quantile(cpuData$PRP)
boxplot(cpuData$PRP,
        main = "Boxplot of published relative performance",
        ylab = "Performance (P.)") 
```
  
    

boxplot of the estimated relative performance from original article
```{r}
quantile(cpuData$ERP)
boxplot(cpuData$ERP,
        main = "Boxplot of estimated relative performance from original article",
        ylab = "Performance (P.)") 
```
  
  
##Histograms
Max and Min memory in kb
```{r}

hist(cpuData$MMAX, xlab = 'Max memory in kb',main = 'Histogram of max memory in kb', border = 'black',col = 'orange' )
hist(cpuData$MMIN, xlab = 'Min memory in kb',main = 'Histogram of min memory in kb', border = 'black',col = 'orange' )
```
  
Cache in kb

```{r}
hist(cpuData$CHMAX, xlab = 'Cache in kb',main = 'Histogram of Cache in kb', border = 'black',col = 'red' )

```
  
  
Histogram of machine cycle in nanoseconds
```{r}
hist(cpuData$MYCT, xlab = 'Machine Cycle in kb/nanoseconds',main = 'Histogram of Machine Cycle', border = 'black',col = 'green' )
```
  
  
The nex histograms show the performance, both estimated and publicated

```{r}
hist(cpuData$PRP, xlab = 'Publicated performance in kb/nanoseconds',main = 'Histogram of Publicated performance', border = 'black',col = 'blue' )
hist(cpuData$ERP, xlab = 'Estimated performance in kb/nanoseconds',main = 'Histogram of Public performance', border = 'black',col = 'blue' )
```

